Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-29 Tex/Old text/chapters/introduction.tex
added citation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%%automated verification
\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19}. During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time. They must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

>>>>

%%automated verification
\textcolor{red}{What is the relation between CPS and PV? We should make it clear already in the beginning...}
Cyber-Physical Systems (CPS) are engineered systems, which are built from, and depend upon, the seamless integration of computational and physical components~\cite{NSF2015,ChavesIBCF19,iet-cps.2018.5006}. During operation, such components must frequently adapt to the operating environment changes (dynamics of the physical processes) faced at run-time. They must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
